Optimizing Abstract Abstract Machines

### 2013-07-01 paper/paper.tex
Missing newline.
Tweak to acks.

We represent change logs as $\msdiff \in \StoreDelta = (\Addr \times
  \Set(\Storeable))^*$. Each $\msto\sqcup[\maddr \mapsto \mval{s}]$
 becomes a log addition
$\cons{\ttuple{\maddr}{\mval{s}}}{\msdiff}$, where $\msdiff$ begins
empty ($\mtlst$) for each step. Applying the changes to the full store
is straightforward:
\begin{equation*}
\replay : (\StoreDelta \times \Store) \to (\Store \times \Boolean)
\end{equation*}
\begin{align*}
\replay(\left[ \ttuple{\maddr_i}{\mval{s_i}}, \ldots\right], \msto) &=
\ttuple{\msto'}
       {\diffp(\mval{s_i}, \msto(\maddr_i)) \vee \ldots} \\
\text{ where } \msto' &= {\msto \sqcup [\maddr_i \mapsto \mval{s_i}] \sqcup \ldots}
\diffp(\mval{s}, \mval{s'}) &= \mval{s'} \overset{?}{=} \mval{s} \sqcup \mval{s'}
\end{align*}

@@

We thank Suresh Jagannathan for providing source code to the polymorphic splitting analyzer~\cite{dvanhorn:wright-jagannathan-toplas98} and Ilya Sergey for the introspective pushdown analyzer~\cite{dvanhorn:Earl2012Introspective}.

>>>>

We represent change logs as $\msdiff \in \StoreDelta = (\Addr \times
  \Set(\Storeable))^*$. Each $\msto\sqcup[\maddr \mapsto \mval{s}]$
 becomes a log addition
$\cons{\ttuple{\maddr}{\mval{s}}}{\msdiff}$, where $\msdiff$ begins
empty ($\mtlst$) for each step. Applying the changes to the full store
is straightforward:
\begin{equation*}
\replay : (\StoreDelta \times \Store) \to (\Store \times \Boolean)
\end{equation*}
\begin{align*}
\replay(\left[ \ttuple{\maddr_i}{\mval{s_i}}, \ldots\right], \msto) &=
\ttuple{\msto'}
       {\diffp(\mval{s_i}, \msto(\maddr_i)) \vee \ldots} \\
\text{ where } \msto' &= {\msto \sqcup [\maddr_i \mapsto \mval{s_i}] \sqcup \ldots} \\
\diffp(\mval{s}, \mval{s'}) &= \mval{s'} \overset{?}{=} \mval{s} \sqcup \mval{s'}
\end{align*}

@@

We thank Suresh Jagannathan for providing source code to the
polymorphic splitting
analyzer~\cite{dvanhorn:wright-jagannathan-toplas98} and Ilya Sergey
for the introspective pushdown
analyzer~\cite{dvanhorn:Earl2012Introspective}.  We thank our
anonymous reviewers for their detailed comments.

This material is based on research sponsored by DARPA under the
programs Automated Program Analysis for Cybersecurity
(FA8750-12-2-0106) and Clean-Slate Resilient Adaptive Hosts (CRASH).
The U.S. Government is authorized to reproduce and distribute reprints
for Governmental purposes notwithstanding any copyright notation
thereon.
